Documentation/overview Functional Limits of Agreement

### 2021-06-10 floa_doc.Rmd
Minor changes documentation files
Minor changes to documentation file

## Kurze Zusammenfassung

Aufgabenstellung: Vergleich zweier Messsysteme mit kontinuierlichem Output

@@

+ In looking at limits of agreement, the authors are considering the extent of within pair variation. However, in looking at the point wise limits of agreement, these are defined to incorporate a between pair standard deviation. Even if it was appropriate to utilise between pair variability, the authors should note that it is variances that are additive and not SDs. Perhaps the authors lack of understanding comes from their erroneous assumption (iii).

(iii) Measurement uncertainty can be estimated adequately by bootstrapping the error variance from a sample that consists of a single curve per subject.
If no repeated measurements are included in the sample, an essential error component (intra-individual variance) is ignored. The bootstrap – like any other statistical procedure – cannot solve this problem, as it can only estimate proportions of variance that are contained in the sample.

@@

#### Was meint der Reviewer?

- Although the pointwise approach ignores the temporal dependence, it is not an issue when it comes to estimation. For inference, on the other hand, it should be taken into account

#### Irrtümer der Reviewer!?

@@

#### Mögliche Lösungsansätze

@@

Die FLoA~2SD~ (Roislien et al.) würde ich hingegen erstmal drin lassen, da a. unsere Methode darauf aufbaut und b. die Vorteile unserer Methode so besser veranschaulicht werden können. Zudem kann ich mir vorstellen, dass die Forderung nach einer Vergleichsmethode beim Einreichen eines neuen Papers zwangsläufig irgendwann kommt.

@@

>>>>

## Zusammenfassung

Frage ergab sich ursprünglich im Rahmen der Validierung einer hauseigenen IMU gegenüber einem kamerabasierten Messsystem (Vicon).

@@

+ In looking at limits of agreement, the authors are considering the extent of within pair variation. However, in looking at the point wise limits of agreement, these are defined to incorporate a between pair standard deviation. Even if it was appropriate to utilise between pair variability, the authors should note that it is variances that are additive and not SDs. Perhaps the authors lack of understanding comes from their *erroneous assumption* (iii).

*iii Measurement uncertainty can be estimated adequately by bootstrapping the error variance from a sample that consists of a single curve per subject.*

*If no repeated measurements are included in the sample, an essential error component (intra-individual variance) is ignored. The bootstrap – like any other statistical procedure – cannot solve this problem, as it can only estimate proportions of variance that are contained in the sample.*

Die erwähnte assumption bezieht sich auf eine Grundannahme die im Roislien Paper getroffen wurde und in unserem Paper kritisch aufgegriffen wurde.

@@

#### Fragwürdige Einschätzungen seitens der Reviewer

@@

### Mögliche Lösungsansätze

@@

... siehe dieser Kommentar der Reviewer: Although the pointwise approach ignores the temporal dependence, it is not an issue when it comes to estimation. For inference, on the other hand, it should be taken into account

+ Die FLoA~2SD~ (Roislien et al.) würde ich hingegen erstmal drin lassen, da a. unsere Methode darauf aufbaut und b. die Vorteile unserer Methode so besser veranschaulicht werden können. Zudem kann ich mir vorstellen, dass die Forderung nach einer Vergleichsmethode beim Einreichen eines neuen Papers zwangsläufig irgendwann kommt.

@@

## Sonstiges

+ FLoA~RCB~ als R package

+ Github repository: https://github.com/koda86/floa
